Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-15 articles/cycle/alps-cycle.tex
Add references on flow patterns.

@@

@@

>>>>

    The LGM Alpine ice flow pattern was traditionally described as that of a
    network of interconnected valley glaciers that was primarily controlled by
    subglacial topography. However, the geomorphology shows that ice was thick
    enough to flow accross high mountain passes throughout the mountain range
    \citep[e.g.,][]{Onde.1938, Penck.Bruckner.1909, Jackli.1962, Husen.1985,
    Coutterand.2010, Kelly.etal.2004, Husen.2011}, and even perhaps form
    self-sustained ice domes \citep{Florineth.1998, Florineth.Schluchter.1998,
    Kelly.etal.2004, Bini.etal.2009}.

@@

    Transfluence across col de Montgenèvre was previously questioned
    \citep[Fig.~2]{Cossart.etal.2012}. Transfluence across col de Mont Cenis
    was previoysly described \citep[Fig.~3.18]{Onde.1938, Coutterand.2010}.
    Transfluences across Fernpass and Seefeld are known from the geomorphology
    \citep[Fig.~2.4]{Penck.Bruckner.1909, Husen.2011}. Transfluence across
    Brunigpass was already marked in the maps \citep{Jackli.1962}. There is
    numerous evidence for transfluence across Simplon Pass
    \citep{Kelly.etal.2004}. Ice crossed the Pyhrn Pass \citep{Husen.2004}. Ice
    flew across the Gailberg and Kreuzberg saddles \citep{Husen.1985}. The
    Tagliamento catchment is usually assumed to not have received tranfluences
    from the Drau catchment \citep{Monegato.etal.2007}, but this would not be
    incompatible with reconstructed ice surface elevations in this area
    \citep{Husen.1987}.

@@

%    \citep{Jouvet.etal.2017}
